Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
microtype
reordering of fxp section. Adding note about stability

Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point \todo{add reference}.  
Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
In this paper, we consider systems with a reference signal equal to zero.

@@

\todo{I've moved the following paragraph to this section, from that on safety specs.}
The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and the digital controller. 
%, and the digital reference signal. 
%In this paper, we consider systems with a reference signal equal to zero. 
%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
%and disregarding it in the state equation~\eqref{eq:plant}.
Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{explain and clarify notation.}
to to denote numbers represented with the precision of the digital controller. All other numbers
are represented with the precision of our plant model:
%
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}
%\left\lbrace
%\begin{array}{l}
%u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
%x_{k+1}=Ax_{k}+Bu_{k}
%\end{array}\right.
%\end{equation}

@@

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Discretising continuous space dynamics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

Asymptotic stability boils down to Lyapunov stability and convergence to an equilibrium point\cite{Astrom08} %\todo{add reference}.  
Lyapunov stability requires that model trajectories remain in a neighbourhood of the equilibrium point. 
In the case of closed-loop LTI models as in \eqref{eq:closedloopss}, 
the equilibrium point is the origin (if the reference is equal to zero), or an offset thereof.  
In this paper, we consider systems with a reference signal equal to zero.

@@

@@

\subsubsection{Effect on safety specification and stability}
The states values must be computed considering the digital controller error, i.e., the error introduced by the ADC and the digital controller. 
%, and the digital reference signal. 
%In this paper, we consider systems with a reference signal equal to zero. 
%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
%and disregarding it in the state equation~\eqref{eq:plant}.
Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{explain and clarify notation.}
to to denote numbers represented with the precision of the digital controller. All other numbers
are represented with the precision of our plant model:
%
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}

We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is $\delta$ away from the desired equilibrium point, see Appendix. In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification. Hence, it is sufficient to synthesise a stable controller based on infinite precision, and then verify safety.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Discretizing continuous space dynamics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
